Energy and exergy analysis of a cruise ship

### 2017-07-05 Manuscript/Manuscript.tex
More updates on the python files

Here we show and discuss about some interesting values. 
\begin{itemize}
	\item External temperature
	\item Sea water temperature
	\item Ship speed
	\item Other
\end{itemize}

@@

>>>>

In this section, we observe and analyze direct measurements from ship systems, with no pre-processing, that are expected to have an influence on the energy analysis.

Figure XX represents the distribution and the evolution over the year of the ambient air and sea water temperature. The relatively low temperatures that are experienced by the case study ship during its operations suggest that heating demand can be expected to be higher than cooling demand. On the other hand, the fact that, in summer, air temperatures reach up to 26 degrees Celsius justify the existence of an HVAC unit that can also operate in cooling mode.

Figure XX represents the distribution of the ship speed, both in terms of statistical distribution and in terms of a reference 24h period. The ship operates almost for the entire year according to a fix schedule.

NOTE: It would be interesting to find a way to categorize all periods in each phase (sailing in the archipelago - sailing at open sea) and trying to analyze statistically their duration / mean power / etc.

\begin{itemize}
	\item External temperature
	\item Sea water temperature
	\item Ship speed
\end{itemize}

@@

Estimated heat demand
Maximum heat demand 
Minimum heat demand
